Hochschild cohomology of torus-equivariant D-modules

### 2015-06-24 paper.tex
Remove space at end of line.
Improvements.

\let\stack\mathbf
\let\bar\overline

@@

\newcommand\Γsub[1]{\Gamma_{\mkern-3mu#1}}

@@

Given a manifold $X$ and a category of sheaves on $X$, microlocal geometry asks whether these sheaves can be localized not just on $X$ but also with respect to codirections, i.e.~on the cotangent space $T^*X$.
For example, for constructible sheaves this leads to the notion of microsupport discussed in detail in \cite{KashiwaraSchapira:1994:SheavesOnManifolds}.
More generally, given a category of sheaves on a space $X$, we can ask whether it is possible to localize them on some space that is strictly larger than $X$ itself.

@@

We are led to consider the universal algebra acting on the category with this construction, i.e.~the \emph{Hochschild cohomology} of $\cat C$.
For a complete (pre-triangulated) dg category $\cat C$ the Hochschild cohomology is the dg algebra of derived endomorphisms of the identity functor of $\cat C$:
\[
    \HCoh(\cat C)
    = \operatorname{\mathbf{R}Hom}(\id[\cat C], \id[\cat C])
    = \Hom_{\cat{Funct}(\cat C, \cat C)}(\id[\cat C], \id[\cat C]).
\]
The ring $R = \bigoplus \operatorname{HH}^{2n}(\HCoh(\cat C)$ is commutative and hence one can define for each $A ∈ \cat C$ the support $\supp_R A$ as a subset of $\Spec R$.
Thus understanding the Hochschild cohomology of a dg category can be an important step to understanding the category itself.

This construction, applied to the category of (ind-)coherent sheaves on a (quasismooth, dg-) scheme yields the singular support of coherent sheaves introduced in \cite{ArinkinGaitsgory:2015:SingularSupport}.
More concretely, the authors used this notion of singular support for the category $\catIndCoh{\LocSys_G}$ in their formulation of the geometric Langlands conjecture.
By Langlands duality, one should then have a matching support theory for the category $\catDMod{\Bun_G}$ and the question arises whether it is possible to formulate this theory in a way that is intrinsic to D-modules.

@@

By Verdier duality and adjunction we can always rewrite \eqref{eq:intro:d-mod-hcoh} as
\[
    \HCoh(\catDMod{\stack X}) \cong
    \opalg{\Hom_{\catDMod{X}}(k_{\stack X}, Δ^!Δ_!k_{\stack X})} =
    \opalg{\ΓdR(\stack X, Δ^!Δ_!k_{\stack X})}.
\]
It is now tempting to look at the Cartesian square
\[
    \begin{tikzcd}
        \ls \stack X \arrow[r, "p₁"] \arrow[d, "p₂"] & \stack X \arrow[d, "Δ"] \\
        \stack X \arrow[r, "Δ"] & \stack X × \stack X
    \end{tikzcd}
\]
where
\[
    \ls \stack X = \stack X ×\limits_{\stack X × \stack X} \stack X
\]
is the (derived) loop space of $\stack X$ and try to express the Hochschild cohomology as the cohomology of some sheaf on $\ls \stack X$.
Naively we could expect the existence of an isomorphism
\begin{equation}
    \label{eq:intro:naive}
    \ΓdR(\stack X, Δ^!Δ_!k_{\stack X}) \cong
    \ΓdR(\stack X, p_{2,!}p₁^! k_{\stack X}).
\end{equation}
Unfortunately, the two sides are in general not isomorphic (the stack $\stack X = \ps1/\Ga$ is an easy counter-example).

@@

We fix an algebraically closed base field $k$ of characteristic $0$.
All stacks will be assumed to be algebraic QCA stacks over $k$.
As we will summarize below, the QCA condition ensures that the category of D-modules on stacks is well-behaved.
In particular for any stack $\stack X$ we have:
\begin{itemize}
    \item The diagonal morphism $Δ\colon \stack X → \stack X × \stack X$ is schematic.
    \item There exists a scheme $Z$ with a smooth and surjective map $Z → \stack X$.
    \item $\stack X$ is quasi-compact.
    \item The automorphism groups of the geometric points of $\stack X$ are affine.
    \item The loop space (or inertia stack) $\ls \stack X = \stack X ×_{\stack X × \stack X} \stack X$ is of finite presentation over $\stack X$.
\end{itemize}
The first two conditions ensure that the stack is algebraic, the other three that it is quasi-compact with affine automorphism group (QCA).
For details on QCA stacks we refer to~\cite{DrinfeldGaitsgory:2013:FinitenessQuestions}.
Every quotient of a scheme of finite type over $k$ by an affine algebraic group is a QCA stack, and we will be mainly interested in these.

@@

It is often useful to consider the pullback of a D-module on $\stack X$ to a smooth cover.

@@

@@

Recall now that we assume $Δ$ to be schematic schematic and that the dualizing module $ω_{\stack X}$ is always holonomic.
Thus we have $\dualize Δ_* ω_{\stack X} = Δ_! k_{\stack X}$.
With this we observe that
\begin{align*}
    \HCoh\bigl(\catDMod{\stack X}\bigr)
    & = \Hom_{\catDMod{\stack X × \stack X}}(Δ_* ω_{\stack X},\, Δ_* ω_{\stack X}) & &\text{(Lemma~\ref{lem:pre:hcoh})} \\
    & = \opalg{\Hom_{\catDMod{\stack X × \stack X}}(Δ_! k_{\stack X},\, Δ_! k_{\stack X})} & & \text{(duality)} \\
    & = \opalg{\Hom_{\catDMod{\stack X × \stack X}}(k_{\stack X},\, Δ^! Δ_! k_{\stack X})} & & \text{(adjunction)} \\
    & = \opalg{\ΓdR\bigl(\stack X,\, Δ^! Δ_! k_{\stack X}\bigr)},
\end{align*}
where the algebra structure on $\ΓdR\bigl(\stack X,\, Δ^! Δ_! k_{\stack X}\bigr) = \Hom_{\catDMod{\stack X × \stack X}}(k_{\stack X},\, Δ^! Δ_! k_{\stack X})$ is the one induced by the $(Δ_!,Δ^!)$-adjunction monad.
Consider the Cartesian square
\[
    \begin{tikzcd}
        \ls{\stack X} \arrow[r, "p₁"] \arrow[d, "p₂"] & \stack X \arrow[d, "Δ"] \\
        \stack X \arrow[r, "Δ"] & \stack X × \stack X
    \end{tikzcd}
\]
Let us assume for the moment that $Δ$ (and hence $p_i$) was proper.
Then $Δ_* = Δ_!$ and $p_{2,*} = p_{2,!}$ and by Section~\ref{sec:pre:monads} we have an isomorphism of monads
\begin{equation}
    \label{eq:central_iso}
    p_{2,!} p₁^! → Δ^!Δ_!,
\end{equation}
which induces an isomorphism of algebras
\[
    \ΓdR\bigl(\stack X,\, p_{2,!} p₁^! k_{\stack X}\bigr)
    →
    \ΓdR\bigl(\stack X,\, Δ^! Δ_! k_{\stack X}\bigr).
\]
Of course, if $X$ is not an algebraic space, then $Δ$ is not proper (nor is it in general smooth).
Thus in general \eqref{eq:central_iso} is not an isomorphism and there is no canonical structure of monad on $p_{2,!} p₁^!$.
We would like to apply Lemma~\ref{lem:pre:groupoid_monad_hol} to construct a monad in special cases.
Thus the goal of the next section is to give a criterion for the assumptions of Lemma~\ref{lem:pre:groupoid_monad_hol}, i.e.~for base change to hold.

@@

In the preceding section we simply assumed that a relative compactification of the diagonal exists.
We will now construct such a compactification for quotient stacks.
Thus let $X$ be a scheme of finite type over $k$ and let $G$ be an affine algebraic group over $k$ acting on $X$.
Let $\stack X = X/G$ be the corresponding quotient stack.

@@

Instead of viewing $Γ$ as the graph of $(\proj2, a)$ we can drop the third factor and regard $Γ$ as the graph of the action map, i.e.
\[
    \Γsub{a} = \bigl\{(g, x, gx) ∈ G × X × X\bigr\}.
\]
The closure $\bar{ \Γsub{a}}$ of $\Γsub a$ in $\bar G × X × X$ identifies with $\bar Γ$.
Thus for ease of notation we will from now on always set $Γ = \Γsub a$ and $\bar Γ = \bar{\Γsub a}$.

\begin{Def}
    Let $\stack X = X/G$.
    With the above construction we set
    \[
        \bar{\stack X} = \rquot{\bar Γ}{G×G}.
    \]
    We have an open embedding $j\colon X \hookrightarrow \bar{\stack X}$ and a proper morphism $\bar Δ\colon \bar{\stack X} → \stack X × \stack X$ induced by the map $f$ above, such that $Δ = \bar Δ ∘ j$.
\end{Def}

\begin{Rem}
    In the case of $G = \Gm$ the compactification $\bar Γ$ is explicitly described in \cite{DrinfeldGaitsgory:2014:OnATheoremOfBraden}.
    In particular, if $X$ is smooth it is shown there that $\bar Γ$ is smooth over $\bar G = \ps1$.
    It is possible to extend the methods of \cite{DrinfeldGaitsgory:2014:OnATheoremOfBraden} to quotients by higher dimensional tori.
    The resulting constructions are highly useful for doing explicit computations.
\end{Rem}

It is useful to consider only partial compactifications.
For this let $V$ be a $G$-stable subvariety of $\bar G$ and let $\bar{\Γsub V}$ be the closure of $Γ$ in $G × V$.
We set
\[
    \bar{\stack X}_V = \rquot{\bar{\Γsub V}}{G×G}.
\]
Clearly, if $\left\{V_i\right\}$ is an open cover of $\bar G$ by $G$-stable subvarieties, then $\left\{\bar{\stack X}_{V_i}\right\}$ is an open cover of $\bar{\stack X}$.

@@

Let $\stack X = X/G$ be a quotient stack as before.
For any morphism of stacks $h\colon \stack Y → \stack X$ we set $\lsY{\stack X} = \stack X ×_{\stack X × \stack X} \stack Y$.
Thus we have the Cartesian diagram
\[
    \begin{tikzcd}
        \lsY \stack X \arrow[r, "q_{\stack Y}"] \arrow[d] & \stack X \arrow[d, "Δ"] \\
        \stack Y \arrow[r, "Δ∘h"] & \stack X × \stack X
    \end{tikzcd}
\]
Let us fix a relative compactification $\bar Δ \colon \bar{\stack X} → \stack X × \stack X$ as in Section~\ref{sec:base-change:compactification}.
Using the notation of Section~\ref{sec:base-change:cone} we set $\clsY{\stack X} = \bar{\stack X} ×_{\stack X × \stack X} \stack Y$ and $\lscY{\stack X} = {\stack X}^c ×_{\stack X × \stack X} \stack Y$.
We let $\bar q_{\stack Y}\colon \clsY\stack X → \bar{\stack X}$ be the projection morphism and $i_{\stack Y}\colon \lscY\stack X \hookrightarrow \clsY\stack X$ the inclusion.
Thus we have the following central diagram
\[
    \begin{tikzcd}
        \lsY\stack X \arrow[r, hook] \arrow[d, "q_{\stack Y}"] & \clsY\stack X \arrow[d, "\bar q_{\stack Y}"] & \lscY\stack X \arrow[l, hook', "i_{\stack Y}"'] \arrow[d] \\
        \stack X \arrow[r, hook, "j"] & \bar{\stack X} & \stack X^c \arrow[l, hook']
    \end{tikzcd}
\]

@@

\begin{proof}
    We apply Lemma~\ref{lem:pre:groupoid_monad_hol} to the groupoid $\ls\stack X \rightrightarrows \stack X$.
    Thus we let $\stack G_\cx$ be the simplicial stack with
    \[
        \stack G_i = \underbrace{\ls\stack X ×_{\stack X} \dotsb ×_{\stack X} \ls\stack X}_{\text{$i$ factors}}.
    \]
    Any morphism $F\colon [n] → [m]$ in $\cat{Δ}^{\mathrm{op}}$ induces a diagram
    \[
        \begin{tikzcd}
            \stack G_{n+1} \arrow[d] \arrow[r] & \stack G_{m+1} \arrow[d] \arrow[r] & \stack X \arrow[d, "Δ"] \\
            \stack G_{n} \arrow[r] & \stack G_m \arrow[r] & \stack X × \stack X
        \end{tikzcd}
    \]
    We have to show that base change holds along the left-hand square.
    But by the assumption and Lemma~\ref{lem:base-change-criterion}, base change holds along the outer rectangle and the left-hand square.
    Thus it also holds along the left-hand square.
\end{proof}

\begin{Rem}
    We expect that most quotient stacks are not \goodstack.
    For example, a direct computation shows that Theorem~\ref{thm:main} does not hold for the stack $\ps1/\Ga$, and hence it is not \goodstack.
    For non-\goodstack\ stacks, Lemma~\ref{lem:base-change-criterion} instead gives a description of how much the naive expectation for $\HCoh\bigl(\catDMod{\stack X}\bigr)$ fails.
\end{Rem}

@@

By Lemma~\ref{lem:base-change:cover}, it suffices to prove Theorem~\ref{thm:torus:is-good} for stacks $X/G$ with $X$ affine.
We fix an isomorphism $G \cong \Gm^n$ and compactify $G$ to $\bigl(\ps1\bigr)^n$.
The variety $\bigl(\ps1\bigr)^n$ can be covered by $G$-equivariant open subvarieties of the form $\as n$.
Thus by Lemma~\ref{lem:base-change:cover-by-relative-compactifications}, it suffices to check \goodness\ for the relative compactification $\Gm^n \subseteq \as n$.
To simplify notation, we drop the subscript $\as n$ from the notation and set $\bar{\stack X} = \bar{\stack X}_{\as n}$ and similarly for the various maps.

We fix a quotient stack $\stack Y = Y/G$ and a morphism $h\colon \stack Y → \stack X$, induced by a $G$-equivariant morphism $\schemeh\colon Y → X$.
According to Lemma~\ref{lem:base-change:scheme-cover}, rather than working with stack directly, we can base change to schemes.
We will use the notation of Lemma~\ref{lem:base-change:scheme-cover}, but for ease of notation we will drop the subscript $\stack Y$ and the primes from the maps.
\dropprimes%
Thus we are concerned with the diagram
\[
    \begin{tikzcd}
        \schemelscY \stack X \arrow[r, hook, "\schemei"] &
        \schemeclsY \stack X \arrow[r, "\schemebarq"] &
        \bar Γ &
        Γ \arrow[l, hook', "\schemej"'],
    \end{tikzcd}
\]
where we have to show that $\schemei^* \schemebarq^! \schemej_!$ vanishes on $\catDModHolMon{Γ}{G×G}$.

@@

Let $S$ be closed subgroup of $G$ and let $X^S$ be the $S$-fixed points of $X$.
Since $G$ is Abelian (and hence $S$ a normal subgroup), $X^S$ is a $G$-stable closed subscheme of $X$.
Hence $X^S/G$ is a closed substack of $\stack X$.
Let $\bar S$ be the closure of $S$ in $\bar G = \as n$ and consider the space
\[
    \schemecls[S]_{\stack Y} \stack X =
    \biggl\{
        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \schemeh(y) ∈ X^S,\, \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁\bar S
    \biggr\}
    ⊆ 
    \schemecls_{\stack Y} \stack X.
\]

@@

    We write $G \cong G₁ × S₁$ for some subgroup $G₁$ of $G$.
    This given a corresponding decomposition of the monad $\bar G \cong \as n$ as $\bar G = \bar G₁ \bar S₁$.
    Let $H' = \bar G₁ H$.
    We note that $G ∩ H' = \emptyset$.

@@

\begin{proof}[Proof of Theorem~\ref{thm:torus:is-good}]
    By Lemma~\ref{lem:stabilizers_cover} the closed subschemes $\schemeclsY[S]\stack X$ for $S ∈ \Stab \stack X$ cover $\schemeclsY\stack X$.
    If $S₁,\, S₂ ∈ \Stab\stack X$, then
    \[
        \schemeclsY[S₁]\stack X ∩ \schemeclsY[S₂]\stack X = 
        \schemeclsY[S₁∩S₂,\, S₁S₂].
    \]
    Thus the theorem follows from an iterated Mayer-Vietoris argument using Lemmas~\ref{lem:key_for_stablizier}.
\end{proof}

>>>>

\let\stack\mathbf
\let\shortbar\bar
\let\bar\overline

@@

\newcommand\Γsub[1]{\Gamma_{\mkern-3mu#1}}
\newcommand\barΓsub[1]{\bar{\Gamma}_{\mkern-3mu#1}}

@@

Given a manifold $X$ and a category of sheaves on $X$, microlocal geometry asks whether the sheaves can be localized not just on $X$ but also with respect to codirections, i.e.~on the cotangent space $T^*X$.
For example, for constructible sheaves this leads to the notion of microsupport discussed in detail in \cite{KashiwaraSchapira:1994:SheavesOnManifolds}.
More generally, given a category of sheaves on a space $X$, we can ask whether it is possible to localize them on some space that is strictly larger than $X$ itself.

@@

We are led to consider the universal algebra acting on $\cat C$ by this construction, i.e.~the \emph{Hochschild cohomology} of $\cat C$.
For a complete (pre-triangulated) dg category $\cat C$ the Hochschild cohomology is the dg algebra of derived endomorphisms of the identity functor of $\cat C$:
\[
    \HCoh(\cat C)
    = \operatorname{\mathbf{R}Hom}(\id[\cat C], \id[\cat C])
    = \Hom_{\cat{Funct}(\cat C, \cat C)}(\id[\cat C], \id[\cat C]).
\]
The ring $R = \bigoplus \operatorname{HH}^{2n}(\cat C)$ is commutative and hence one can define for each $A ∈ \cat C$ the support $\supp_R A$ as a subset of $\Spec R$.
Thus understanding the Hochschild cohomology of a dg category can be an important step to understanding the category itself.

This construction, applied to the category of (ind-)coherent sheaves on a (quasismooth, dg-) scheme, yields the singular support of coherent sheaves introduced in \cite{ArinkinGaitsgory:2015:SingularSupport}.
More concretely, the authors used this notion of singular support for the category $\catIndCoh{\LocSys_G}$ in their formulation of the geometric Langlands conjecture.
By Langlands duality, one should then have a matching support theory for the category $\catDMod{\Bun_G}$ and the question arises whether it is possible to formulate this theory in a way that is intrinsic to D-modules.

@@

By Verdier duality and adjunction we can always rewrite \eqref{eq:intro:d-mod-hcoh} as
\[
    \HCoh(\catDMod{\stack X}) \cong
    \opalg{\Hom_{\catDMod{X}}(k_{\stack X}, Δ^!Δ_!k_{\stack X})} =
    \opalg{\ΓdR(\stack X, Δ^!Δ_!k_{\stack X})}.
\]
It is now tempting to look at the Cartesian square
\[
    \begin{tikzcd}
        \ls \stack X \arrow[r, "p₁"] \arrow[d, "p₂"] & \stack X \arrow[d, "Δ"] \\
        \stack X \arrow[r, "Δ"] & \stack X × \stack X
    \end{tikzcd}
\]
where
\[
    \ls \stack X = \stack X ×\limits_{\stack X × \stack X} \stack X
\]
is the (derived) loop space of $\stack X$ and try to express the Hochschild cohomology as the cohomology of some sheaf on $\ls \stack X$.
We could expect the existence of an isomorphism
\begin{equation}
    \label{eq:intro:naive}
    \ΓdR(\stack X, Δ^!Δ_!k_{\stack X}) \cong
    \ΓdR(\stack X, p_{2,!}p₁^! k_{\stack X}).
\end{equation}
We refer to this as the \enquote{naive expectation}.
Unfortunately, the two sides are in general not isomorphic (the stack $\stack X = \ps1/\Ga$ is an easy counter-example).

@@

We fix an algebraically closed base field $k$ of characteristic $0$.
All stacks will be assumed to be algebraic QCA stacks over $k$.
As we will summarize below, the QCA condition ensures that the category of D-modules on stacks is well-behaved.
Thus by definition for any stack $\stack X$ we have:
\begin{itemize}
    \item The diagonal morphism $Δ\colon \stack X → \stack X × \stack X$ is schematic.
    \item There exists a scheme $Z$ with a smooth and surjective map $Z → \stack X$.
    \item $\stack X$ is quasi-compact.
    \item The automorphism groups of the geometric points of $\stack X$ are affine.
    \item The loop space (or inertia stack) $\ls \stack X = \stack X ×_{\stack X × \stack X} \stack X$ is of finite presentation over $\stack X$.
\end{itemize}
The first two conditions ensure that the stack is algebraic, the other three that it is quasi-compact with affine automorphism group (QCA).
For details on QCA stacks we refer to~\cite{DrinfeldGaitsgory:2013:FinitenessQuestions}.
Every quotient of a scheme of finite type over $k$ by an affine algebraic group is a QCA stack, and we will be mainly interested in these.

@@

It is often useful to consider the pullback of a D-module on $\stack X$ to a smooth cover.
For quotient stacks we give the resulting subcategory a special name.

@@

For reference, we state the following theorem which will be a crucial ingredient in the proof of Theorem~\ref{thm:main}.

@@

Recall now that we assume $Δ$ to be schematic and that the dualizing module $ω_{\stack X}$ is always holonomic.
Thus we have $\dualize Δ_* ω_{\stack X} = Δ_! k_{\stack X}$.
With this we observe that
\begin{align*}
    \HCoh\bigl(\catDMod{\stack X}\bigr)
    & = \Hom_{\catDMod{\stack X × \stack X}}(Δ_* ω_{\stack X},\, Δ_* ω_{\stack X}) & &\text{(Lemma~\ref{lem:pre:hcoh})} \\
    & = \opalg{\Hom_{\catDMod{\stack X × \stack X}}(Δ_! k_{\stack X},\, Δ_! k_{\stack X})} & & \text{(duality)} \\
    & = \opalg{\Hom_{\catDMod{\stack X × \stack X}}(k_{\stack X},\, Δ^! Δ_! k_{\stack X})} & & \text{(adjunction)} \\
    & = \opalg{\ΓdR\bigl(\stack X,\, Δ^! Δ_! k_{\stack X}\bigr)},
\end{align*}
where the algebra structure on $\ΓdR\bigl(\stack X,\, Δ^! Δ_! k_{\stack X}\bigr) = \Hom_{\catDMod{\stack X × \stack X}}(k_{\stack X},\, Δ^! Δ_! k_{\stack X})$ is the one induced by the $(Δ_!,Δ^!)$-adjunction monad.
Consider the Cartesian square
\[
    \begin{tikzcd}
        \ls{\stack X} \arrow[r, "p₁"] \arrow[d, "p₂"] & \stack X \arrow[d, "Δ"] \\
        \stack X \arrow[r, "Δ"] & \stack X × \stack X
    \end{tikzcd}
\]
Let us assume for the moment that $Δ$ (and hence $p_i$) was proper.
Then $Δ_* = Δ_!$ and $p_{2,*} = p_{2,!}$ and by Section~\ref{sec:pre:monads} we have an isomorphism of monads
\begin{equation}
    \label{eq:central_iso}
    p_{2,!} p₁^! → Δ^!Δ_!,
\end{equation}
which induces an isomorphism of algebras
\[
    \ΓdR\bigl(\stack X,\, p_{2,!} p₁^! k_{\stack X}\bigr)
    →
    \ΓdR\bigl(\stack X,\, Δ^! Δ_! k_{\stack X}\bigr).
\]
Of course, if $X$ is not an algebraic space, then $Δ$ is not proper (nor is it in general smooth).
Thus in general \eqref{eq:central_iso} is not an isomorphism and there is no canonical structure of monad on $p_{2,!} p₁^!$.
We would like to apply Lemma~\ref{lem:pre:groupoid_monad_hol} to construct a monad in special cases.
Thus the goal of the next section is to give a criterion for the assumptions of Lemma~\ref{lem:pre:groupoid_monad_hol}, i.e.~for base change to hold.

@@

In the preceding section we simply assumed that a relative compactification of the given map exists.
We will now construct such a compactification for the diagonal map of a quotient stack.
Thus let $X$ be a scheme of finite type over $k$ and let $G$ be an affine algebraic group over $k$ acting on $X$.
Let $\stack X = X/G$ be the corresponding quotient stack.

@@

Instead of viewing $Γ$ as the graph of $(\proj2, a)$ we can drop the third factor and regard $Γ$ as the graph of the action map, i.e.
\[
    \Γsub{a} = \bigl\{(g, x, gx) ∈ G × X × X\bigr\}.
\]
The closure $\barΓsub{a}$ of $\Γsub a$ in $\bar G × X × X$ identifies with $\bar Γ$.
Thus for ease of notation we will from now on always set $Γ = \Γsub a$ and $\bar Γ = \barΓsub{a}$.

\begin{Def}
    Let $\stack X = X/G$.
    With the above construction we set
    \[
        \bar{\stack X} = \rquot{\bar Γ}{G×G}.
    \]
    We have an open embedding $j\colon X \hookrightarrow \bar{\stack X}$ and a proper morphism $\shortbar Δ\colon \bar{\stack X} → \stack X × \stack X$ induced by the map $f$ above, such that $Δ = \shortbar Δ ∘ j$.
\end{Def}

\begin{Rem}
    In the case of $G = \Gm$ the compactification $\bar Γ$ is explicitly described in \cite{DrinfeldGaitsgory:2014:OnATheoremOfBraden}.
    In particular, if $X$ is smooth it is shown there that $\bar Γ$ is smooth over $\bar G = \ps1$.
    It is possible to extend the methods of \cite{DrinfeldGaitsgory:2014:OnATheoremOfBraden} to quotients by higher dimensional tori.
    The resulting constructions are useful for doing explicit computations.
\end{Rem}

It is useful to consider only partial compactifications.
For this let $V$ be a $G$-stable subvariety of $\bar G$ and let $\barΓsub{V}$ be the closure of $Γ$ in $G × V$.
We set
\[
    \bar{\stack X}_V = \rquot{\barΓsub{V}}{G×G}.
\]
Clearly, if $\left\{V_i\right\}$ is an open cover of $\bar G$ by $G$-stable subvarieties, then $\left\{\bar{\stack X}_{V_i}\right\}$ is an open cover of $\bar{\stack X}$.

@@

Let $\stack X = X/G$ be a quotient stack as before.
For any morphism of stacks $h\colon \stack Y → \stack X$ we set $\lsY{\stack X} = \stack X ×_{\stack X × \stack X} \stack Y$.
Thus we have the Cartesian diagram
\[
    \begin{tikzcd}
        \lsY \stack X \arrow[r, "q_{\stack Y}"] \arrow[d] & \stack X \arrow[d, "Δ"] \\
        \stack Y \arrow[r, "Δ∘h"] & \stack X × \stack X
    \end{tikzcd}
\]
Let us fix a relative compactification $\shortbar Δ \colon \bar{\stack X} → \stack X × \stack X$ as in Section~\ref{sec:base-change:compactification}.
Using the notation of Section~\ref{sec:base-change:cone} we set $\clsY{\stack X} = \bar{\stack X} ×_{\stack X × \stack X} \stack Y$ and $\lscY{\stack X} = {\stack X}^c ×_{\stack X × \stack X} \stack Y$.
We let $\bar q_{\stack Y}\colon \clsY\stack X → \bar{\stack X}$ be the projection morphism and $i_{\stack Y}\colon \lscY\stack X \hookrightarrow \clsY\stack X$ the inclusion.
Thus we have the following central diagram
\[
    \begin{tikzcd}
        \lsY\stack X \arrow[r, hook] \arrow[d, "q_{\stack Y}"] & \clsY\stack X \arrow[d, "\bar q_{\stack Y}"] & \lscY\stack X \arrow[l, hook', "i_{\stack Y}"'] \arrow[d] \\
        \stack X \arrow[r, hook, "j"] & \bar{\stack X} & \stack X^c \arrow[l, hook']
    \end{tikzcd}
\]

@@

\begin{proof}
    We apply Lemma~\ref{lem:pre:groupoid_monad_hol} to the groupoid $\ls\stack X \rightrightarrows \stack X$.
    Thus we let $\stack G_\cx$ be the simplicial stack with
    \[
        \stack G_i = \underbrace{\ls\stack X ×_{\stack X} \dotsb ×_{\stack X} \ls\stack X}_{\text{$i$ factors}}.
    \]
    Any morphism $F\colon [n] → [m]$ in $\cat{Δ}^{\mathrm{op}}$ induces a diagram
    \[
        \begin{tikzcd}
            \stack G_{n+1} \arrow[d] \arrow[r] & \stack G_{m+1} \arrow[d] \arrow[r] & \stack X \arrow[d, "Δ"] \\
            \stack G_{n} \arrow[r] & \stack G_m \arrow[r] & \stack X × \stack X
        \end{tikzcd}
    \]
    We have to show that base change holds along the left-hand square.
    But by the assumption and Lemma~\ref{lem:base-change-criterion}, base change holds along the outer rectangle and the right-hand square.
    Thus it also holds along the left-hand square.
\end{proof}

\begin{Rem}
    We expect that most quotient stacks are not \goodstack.
    For example, a direct computation shows that Theorem~\ref{thm:main} does not hold for the stack $\ps1/\Ga$, and hence it is not \goodstack.
    For non-\goodstack\ stacks, the sheaf $i_{\stack X}^* \bar q_{\stack X}^! j_! k_{\stack X}$ instead gives a measurement for the failure of the naive expectation for $\HCoh\bigl(\catDMod{\stack X}\bigr)$.
\end{Rem}

@@

By Lemma~\ref{lem:base-change:cover}, it suffices to prove Theorem~\ref{thm:torus:is-good} for stacks $X/G$ with $X$ affine.
We fix an isomorphism $G \cong \Gm^n$ and compactify $G$ to $\bigl(\ps1\bigr)^n$.
The variety $\bigl(\ps1\bigr)^n$ can be covered by $G$-equivariant open subvarieties of the form $\as n$.
Thus by Lemma~\ref{lem:base-change:cover-by-relative-compactifications}, it suffices to check \goodness\ for the partial compactification $\Gm^n \subseteq \as n$.
To simplify notation, we drop the subscript $\as n$ from the notation and set $\bar{\stack X} = \bar{\stack X}_{\as n}$ and similarly for the various maps.

We fix a quotient stack $\stack Y = Y/G$ and a morphism $h\colon \stack Y → \stack X$, induced by a $G$-equivariant morphism $\schemeh\colon Y → X$.
According to Lemma~\ref{lem:base-change:scheme-cover}, rather than working directly with the stacks, we can base change to schemes.
We will use the notation of Lemma~\ref{lem:base-change:scheme-cover}, but for ease of notation we will drop the subscript $\stack Y$ and the primes from the maps.
\dropprimes%
Thus we are concerned with the diagram
\[
    \begin{tikzcd}
        \schemelscY \stack X \arrow[r, hook, "\schemei"] &
        \schemeclsY \stack X \arrow[r, "\schemebarq"] &
        \bar Γ &
        Γ \arrow[l, hook', "\schemej"'],
    \end{tikzcd}
\]
where we have to show that $\schemei^* \schemebarq^! \schemej_!$ vanishes on $\catDModHolMon{Γ}{G×G}$.

@@

Let $S$ be closed subgroup of $G$ and let $X^S$ be the $S$-fixed points of $X$.
Since $G$ is Abelian (and hence $S$ a normal subgroup), $X^S$ is a $G$-stable closed subscheme of $X$.
Hence $X^S/G$ is a closed substack of $\stack X$.
Let $\bar S$ be the closure of $S$ in $\bar G = \as n$ and consider the closed subspace
\[
    \schemecls[S]_{\stack Y} \stack X =
    \biggl\{
        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \schemeh(y) ∈ X^S,\, \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁\bar S
    \biggr\}
    ⊆
    \schemecls_{\stack Y} \stack X.
\]

@@

    We write $G \cong G₁ × S₁$ for some subgroup $G₁$ of $G$.
    This gives a corresponding decomposition of the monoid $\bar G \cong \as n$ as $\bar G = \bar G₁ \bar S₁$.
    Let $H' = \bar G₁ H$.
    We note that $G ∩ H' = \emptyset$.

@@

\begin{proof}[Proof of Theorem~\ref{thm:torus:is-good}]
    By Lemma~\ref{lem:stabilizers_cover} the closed subschemes $\schemeclsY[S]\stack X$ for $S ∈ \Stab \stack X$ cover $\schemeclsY\stack X$.
    If $S₁,\, S₂ ∈ \Stab\stack X$, then
    \[
        \schemeclsY[S₁]\stack X ∩ \schemeclsY[S₂]\stack X =
        \schemeclsY[S₁∩S₂,\, S₁S₂].
    \]
    Thus the theorem follows from an iterated Mayer-Vietoris argument using Lemma~\ref{lem:key_for_stablizier}.
\end{proof}
